---
title: "Exploring the BRFSS data"
output:
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
  pdf_document: default
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
library(knitr)
library(kableExtra)
require(gridExtra)

```

### Load data


```{r load-data}

load("brfss2013.RData")
```

* * *

## Part 1: Data
The data provided by BRFSS of its ongoing surveillance system designed to measure behavioral risk factors for non-institutionalized adult population residing in the US is an example of **retrospective sampling model**. 

Data is being collected from every state by dialing a randomly selected phone number which ensures **random sampling**. However the individual being approached has the power to decline to participate in the study thus introducing **voluntary response bias** into the data.

Moreover this being an observational study, the results can only be generalized & only association can be established between various parameters being studied.

* * *

## Part 2: Research questions

**Research question 1:**
Healthcare expenses have skyrocketed over the past decade and are beyond the reach of people in the low-income bracket. With little to no Healthcare cover, people are at risk of going bankrupt when faced with unexpected health expenses like that being witnessed during the current pandemic.

**Question 1.1:** Does being in the low-income bracket increase one's probability of being at-risk in relation to unexpected healthcare expenses.

What percent of the total population faces this risk is an important parameter that the government needs to keep an eye on.


**Research question 2:**

Being physically active is crucial for ones health. It is a general belief that the participation of an individual in physical activities goes down with ones age. But when evaluated within the people who regularly do some form of workout, does the association hold true? That is,

**Question 2.1:** Within the physically active group, does the amount of physical activity done depend on a person’s age?

**Question 2.2:** Also, does the activity of choice bear an association with their age?

This information would be useful for new Gyms and Health Clubs in deciding the infrastructure (equipment type and volume, requirement of water spa or physiotherapist etc.) of their facility. 

**Research question 3:**
As per the website, [Diabetes.co.uk]( https://www.diabetes.co.uk/Diabetes-Risk-factors.html): obesity, living a sedentary lifestyle, unhealthy eating, high blood pressure, high cholesterol and ageing are the major factors that increase the chances of a person developing Diabetic condition. 

Of the above-mentioned factors, we shall check for correlation between obesity, ageing and  diabetes. This can be broken into 2 parts:

**Question 3.1:** Are obese people more prone to being diabetic.

**Question 3.2:** Does one’s age increase the risk of developing diabetes.

This information can be used by the health agencies in deciding the minimum age after which individuals should be encouraged to get themselves screened periodically.


* * *

## Part 3: Exploratory data analysis

**Research question 1:**

Healthcare expenses have skyrocketed over the past decade and are beyond the reach of people in the low-income bracket. With little to no Healthcare cover, people are at risk of going bankrupt when faced with unexpected health expenses like that being witnessed during the current pandemic.

**Question 1.1:** Does being in the low-income bracket increase one's probability of being at-risk in relation to unexpected healthcare expenses.


The underlying task in this analysis is to first arrive at the **“at-risk”** population which is the population susceptible to bankruptcy when faced with unexpected healthcare expense. This can be derived from two parameters:

1.  **Availability of Healthcare coverage:** Having a healthcover in any form helps an individual deal with major chunk of unexpected medical expenses.
2. **Financially stability:** relates to the ability to cover for additional expenses not covered by healthcover.This would include ability to pay for medication, doctor fees e.g. dental, surgery, & timely payment of other related medical expenses. 

Based on these aspects, the **"At-risk" classification table** is defined as described below:

```{r Creating a classification table}
# Creating a classification table

At_Risk_Table <- matrix(c("Low", "Moderate", "Moderate", "High"),ncol=2,byrow=TRUE)
colnames(At_Risk_Table) <- c("Financially stable","Financially unstable")
rownames(At_Risk_Table) <- c("With Healthcare coverage", "Without Healthcare coverage")
At_Risk_Table <- as.table(At_Risk_Table)

kable(At_Risk_Table) %>%
  add_header_above(c("AT-RISK CLASSIFICATION TABLE"=3))%>%
  kable_styling(bootstrap_options = c("striped", "hover"))



```


**VARIABLES USED IN ANALYSIS:**

**A) DIRECT VARIABLES FROM BRFSS2013 SURVEY DATABASE**

  1. `hlthpln1:` indicates if one has any kind of healthcare coverage, including health insurance, prepaid plans such as HMOs, government plans such as Medicare, or Indian Health Service  
  2. `medcost:` indicates if one needed to see a doctor but could not,  because of cost, in the past 12 months
  3. `medscost:` indicates if there has been a time in the past 12 months when one did not take medication as prescribed because of cost
  4. `medbills:` indicates ones inability to pay-off any overdue medical bills  
  5. `income2:` Annual household income from all sources
  
**B) NEW VARIABLES CALCULATED USING EXISTING VARIABLES**

  1. `fin_stab`: indicates the Financial stability of an individual
  
  2. `at-risk`: classifies the population based on the **"AT-RISK" CLASSIFICATION TABLE**

First, the direct variables of interest are selected from the `brfss2013` database:
```{r R1: Selecting variables of interest}
# Selecting variables of interest

df1<-brfss2013 %>% select(hlthpln1, medcost, medscost, medbills, income2)
summary (df1)

```

Using these direct variables, the two new variables of interest, `fin_stab`,  & `at-risk` are derived.

`fin_stab` is calculated based on the following criteria:

  `fin_stab` = **"Yes"**, An Individual is identified as financially stable if his reading for `medcost`, `medscost` & `medbills` is "No" 
  
  `fin_stab` = **"No"**, the Individual is considered to be at financial risk if his reading for any one or more of the variables `medcost`, `medscost` & `medbills` is "Yes" 
      
```{r Defining Financial stablilty, message = FALSE}

# Creating new variables to define 'Financial Stability' of an individual
df1<-df1 %>%
  mutate(fs_1 = ifelse(medcost=="No" & medbills=="No" & is.na(medscost), "Yes", ifelse(medcost=="No"& medscost=="No"& is.na(medbills),"Yes",ifelse(medscost=="No" & medbills=="No"& is.na(medcost), "Yes", "No"))))
         
df1<-df1 %>%
  mutate(fs_2 = ifelse(medcost=="No" & is.na(medscost) & is.na(medbills), "Yes", "No" ))

df1<-df1 %>%
  mutate(fs_3 = ifelse(medbills=="No" & is.na(medscost) & is.na(medcost), "Yes", ifelse(medscost=="No" & is.na(medcost) & is.na(medbills), "Yes",ifelse(medscost=="No" & medcost=="No" & medbills=="No", "Yes","No" ))))

# Converting cells with NA's to 0
df1$fs_1[which(is.na(df1$fs_1))]<- 0
df1$fs_2[which(is.na(df1$fs_2))]<- 0
df1$fs_3[which(is.na(df1$fs_3))]<- 0

df1<-df1 %>%
  mutate(fin_stab = ifelse(fs_1=="Yes" | fs_2=="Yes" | fs_3=="Yes", "Yes", ifelse(fs_1=="0" & fs_2=="0" & fs_3 == "0", "NA", "No")))
         
df1%>%
  group_by(fin_stab)%>%
  summarise(count=n())

```


Next we derive the `at-risk`variable based on the **"AT-RISK" CLASSIFICATION TABLE**.

```{r Defining At-risk variable, message = FALSE}
# Creating new variable to define 'At-risk' individual
df1<-df1 %>%
mutate(at_risk = ifelse( hlthpln1 =="Yes" & fin_stab =="Yes", "Low risk",ifelse(hlthpln1 == "Yes" & fin_stab =="No", "Moderate risk", ifelse(hlthpln1 == "No" & fin_stab =="Yes", "Moderate risk", ifelse(hlthpln1=="No" & fin_stab == "No", "High risk", "NA")))))

df1%>%
  group_by(at_risk)%>%
  summarise(count=n())

# Deleting NA cells from the data set
df1<-df1%>%
  filter(!is.na(at_risk),at_risk!="NA", !is.na(income2))
```


Side-by-side bar plots are then plotted to examine the association between variables.
```{r R1- Bar plot: Income vs at-risk}
 # Creating Bar plot: Income vs at-risk

ggplot(df1, aes(x=at_risk, fill = income2)) +
  geom_bar(position="dodge", width = 0.6, color="black", size=0.5, alpha = 0.7) + theme(legend.position = "right", axis.text.x = element_text(angle=90, hjust = 0.8))+ labs(x="Income group", y="`AT-RISK` POPULATION", title="INCOME VS AT-RISK")


```

**Summary 1.1:** It can be seen from the plot that the number of people in the **High-risk** category decrease, while an opposite trend in visible for people in the **Low-risk** category.

Thus, the plot does suggest that there is a possible assosciation between one's income group & his/her ability to bear unexpected healthcare expenses.

**Research question 2:** 

Being physically active helps in maintenance of ones health. It is generally believed that the younger generation is much more active than the older generations. But when evaluated within the people who regularly do some form of workout, does this association hold true? That is,

**Question 2.1:** Within the physically active group, does the amount of physical activity done depend on a person’s age?

**Question 2.2:** Also, does the activity of choice bear an association with their age?


**VARIABLES USED IN ANALYSIS:**

**A) DIRECT VARIABLES FROM BRFSS2013 SURVEY DATABASE**

  1. `X_age_g:` indicates the age-group of the individual 
  2. `X_totinda:` indicates if one has or hasn't performed any kind of physical activity in the last 30 days
  3. `exract11` & `exract21:` indicates the top 2 types of physical activities or exercises done by an individual during the past month 
  4. `exeroft1`&`exeroft2:` indicates how many days per week or per month did one take part in the activity during the past month?
  5. `padur1_` & `padur2_:` indicates how many minutes or hours did one work out.
  
**B) NEW VARIABLES CALCULATED USING EXISTING VARIABLES**

  1. `total_mins`: indicates the cumulative value of the weekly minutes spent in performing the top two types of physical activities.

First, the direct variables of interest are selected from the `brfss2013` database:
database:
```{r R2: Selecting variables of interest}
# Selecting variables of interest

df2<-brfss2013%>%
  select(X_age_g, X_totinda,exract11, exeroft1, padur1_,exract21, exeroft2, padur2_)

df2<-df2%>%
  filter(!is.na(X_totinda), X_totinda=="Had physical activity or exercise", !is.na(X_age_g))

summary(df2)
```

Next, the total weekly minutes are calculated by:

1. Standardizing the frequency of exercise,`exeroft1` & `exeroft2`, to activities/week.

2. Converting duration of exercise, `padur1_` & `padur2_` from hours to minutes, where necessary.

3. Combining the average time spent per week doing both the form of activities into a single variable `total_mins`  

```{r Calculating total exercise time}
# Calculating total exercise time 

df2 <- df2 %>%
mutate(days_w1 = ifelse(exeroft1<200,(exeroft1%%100),round({(exeroft1%%100)*12/52},1)))

df2 <- df2 %>%
mutate(days_w2 = ifelse(exeroft2<200,(exeroft2%%100),round({(exeroft2%%100)*12/52},1)))

df2 <- df2 %>%
mutate(total_mins1 = df2$days_w1*df2$padur1_) 

df2 <- df2 %>%
mutate(total_mins2 = df2$days_w2*df2$padur2_) 

df2 <- df2 %>%
  mutate(total_mins2 = ifelse(!is.na(total_mins2), df2$days_w2*df2$padur2_,0))
  
df2 <- df2 %>%
mutate(total_mins = df2$total_mins1 + df2$total_mins2) 
  
```

Now that we have the `total_mins` variable, we can compare the amount of exercise performed by each age-group using a box plot:

```{r R2: Box-Plot - Age Vs minutes}

# Creating Box-Plot - Age Vs minutes
myColors <- ifelse(levels(df2$X_age_g) =="Age 18 to 24", "Red",ifelse(levels(df2$X_age_g) =="Age 25 to 34", "Green",ifelse(levels(df2$X_age_g) =="Age 35 to 44", "Gray",ifelse(levels(df2$X_age_g) =="Age 45 to 54", "White",ifelse(levels(df2$X_age_g) =="Age 55 to 64", "Pink","Yellow")))))

boxplot(df2$total_mins1~df2$X_age_g, col= myColors, range=1.0, varwidth=FALSE, notch=FALSE, outline=FALSE, boxwex=0.6, border=c("blue"), xlab = "", ylab = "Average weekly exercise time in mins  ",las = 2, pars=list(par(mar=c(8,8,4,2))))
mtext("Age of Individual", side=1, line =7)

```

**Summary 2.1:**  
From the Box plot following seem to be evident,  

a. There is a correlation in the amount of time invested exercising and age; however, this correlation is not a linear one.  

b. The trend appears to be highest for the youngest age group, then dips for middle age group (35-54 years) and then picks up with age.


```{r Selecting top 5 for Age group (18 - 24 years)}

# Creating side-by-side plot for top 5 activities per age group

# Code for Age group 18-24 years

v_1<-df2[df2$X_age_g=="Age 18 to 24",,]

v_1<-v_1$exract11

v_1.freq<-table(v_1)

v_1.freq<-sort(v_1.freq, decreasing = TRUE)

v_1.freq<-v_1.freq[1:5]

v_1.df<-as.data.frame(v_1.freq)

p1<-ggplot(v_1.df, aes(v_1, Freq)) + geom_bar(stat = "identity", width = 0.6, color="black", fill="red", size=0.1, alpha = 0.7) + theme(legend.position = "none", axis.text.x = element_text(angle=90, hjust = 0.8))+ labs(x="Age 18 to 24 years", y="Population count", title="") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

```{r Selecting top 5 for remaining Age groups, echo=FALSE}

# Code for Age group 25-34 years

v_2<-df2[df2$X_age_g=="Age 25 to 34",,]

v_2<-v_2$exract11

v_2.freq<-table(v_2)

v_2.freq<-sort(v_2.freq, decreasing = TRUE)

v_2.freq<-v_2.freq[1:5]

v_2.df<-as.data.frame(v_2.freq)

p2<-ggplot(v_2.df, aes(v_2, Freq)) + geom_bar(stat = "identity", width = 0.6, color="black", fill="green", size=0.1, alpha = 0.7) + theme(legend.position = "none", axis.text.x = element_text(angle=90, hjust = 0.8))+ labs(x="Age 25 to 34 years", y="", title="") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

# Code for Age group 35-44 years

v_3<-df2[df2$X_age_g=="Age 35 to 44",,]

##v_3 <- v_3 %>%
  #mutate (exract11 = ifelse(exract11 == "Gardening (spading, weeding, digging, filling)", "Gardening", exract11))

v_3<-v_3$exract11

v_3.freq<-table(v_3)

v_3.freq<-sort(v_3.freq, decreasing = TRUE)

v_3.freq<-v_3.freq[1:5]

v_3.df<-as.data.frame(v_3.freq)

p3<-ggplot(v_3.df, aes(v_3, Freq)) + geom_bar(stat = "identity", width = 0.6, color="black", fill="grey", size=0.1, alpha = 0.7) + theme(legend.position = "none", axis.text.x = element_text(angle=90, hjust = 0.8))+ labs(x="Age 35 to 44 years", y="", title="") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

# Code for Age group 45-54 years

v_4<-df2[df2$X_age_g=="Age 45 to 54",,]

v_4<-v_4$exract11

v_4.freq<-table(v_4)

v_4.freq<-sort(v_4.freq, decreasing = TRUE)

v_4.freq<-v_4.freq[1:5]

v_4.df<-as.data.frame(v_4.freq)

p4<-ggplot(v_4.df, aes(v_4, Freq)) + geom_bar(stat = "identity", width = 0.6, color="black", fill="white", size=0.1, alpha = 0.7) + theme(legend.position = "none", axis.text.x = element_text(angle=90, hjust = 0.8))+ labs(x="Age 45 to 54 years", y="Population count", title="") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

# Code for Age group 55-64 years

v_5<-df2[df2$X_age_g=="Age 55 to 64",,]

v_5<-v_5$exract11

v_5.freq<-table(v_5)

v_5.freq<-sort(v_5.freq, decreasing = TRUE)

v_5.freq<-v_5.freq[1:5]

v_5.df<-as.data.frame(v_5.freq)

p5<-ggplot(v_5.df, aes(v_5, Freq)) + geom_bar(stat = "identity", width = 0.6, color="black", fill="pink", size=0.1, alpha = 0.7) + theme(legend.position = "none", axis.text.x = element_text(angle=90, hjust = 0.8))+ labs(x="Age 55 to 64 years", y="", title="") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

# Code for Age group 65 years or older

v_6<-df2[df2$X_age_g=="Age 65 or older",,]

v_6<-v_6$exract11

v_6.freq<-table(v_6)

v_6.freq<-sort(v_6.freq, decreasing = TRUE)

v_6.freq<-v_6.freq[1:5]

v_6.df<-as.data.frame(v_6.freq)

p6<-ggplot(v_6.df, aes(v_6, Freq)) + geom_bar(stat = "identity", width = 0.6, color="black", fill="yellow", size=0.1, alpha = 0.7) +  theme(legend.position = "none", axis.text.x = element_text(angle=90, hjust = 0.8))+ labs(x="Age 65 & above", y="", title="") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

```{r Side-by-Side bar plots}

# Creating Side-by-Side bar plots

grid.arrange(p1,p2,p3,p4,p5,p6, nrow=2, ncol=3, layout_matrix = rbind(c(1,2,3), c(4,5,6)))
```

**Summary 2.2:**
From the side-by-side plot age does appear to have an influence on the choice of physical activity, with the exception of Walking. 
Running one could deduce is second most popular form of exercise up to 54 years of age; thereafter gardening appears to be more popular. 

**Research question 3:**

As per the website, [Diabetes.co.uk]( https://www.diabetes.co.uk/Diabetes-Risk-factors.html): obesity, living a sedentary lifestyle, unhealthy eating, high blood pressure, high cholesterol and ageing are the major factors that increase the chances of a person developing Diabetic condition. 

Of the above-mentioned factors, we shall check for correlation between obesity, ageing and  diabetes. This can be broken into 2 parts:

**Question 3.1:** Are obese people more prone to being diabetic.

**Question 3.2:** Does one’s age increase the risk of developing diabetes.

To answer this research question, we would:

P1. First explore the data & identify the variables of interest.

P2. Analyse the data to check the correlation between obesity & age with diabetes.

**P1: Data study & conditioning:**

[Obesity]( https://www.medicinenet.com/script/main/art.asp?articlekey=11760) has been defined by the National Institutes of Health (the NIH) as a BMI (Body Mass Index) of 30 and above. (A BMI of 30 is about 30 pounds overweight.) The BMI, a key index for relating body weight to height, is a person's weight in kilograms (kg) divided by their height in meters (m) squared.

In order to conclude whether a person is obese or not, we shall first create a new variable, **BMI** and then create a second variable, **Obese** to categorize them appropriately.

Following is the list of variables used in this analysis:

**DIRECT VARIABLES FROM BRFSS2013 SURVEY DATABASE**

**weight2:** gives weight of the person in pounds or kilograms

**height3:** gives height of the person in ft-inches, meters or centimeters

**diabete3:** provides information regarding the person's diabetic condition as "Yes"; "Yes, but female told only during pergnancy", No, prediabetic or borderline diabetic", "No"

**X_ageg5yr:** gives age of the person in years

**NEW VARIABLES CALCULATED USING EXISTING VARIABLES**

**ht_mtrs:** gives height of the person in meters

**wt_kgs:** gives weight of the person in kilograms (kgs)

**BMI:** gives BMI of the person based on his height & weight

**diabetic:** classifies the person's diabetic condition as "Yes" or "No"

**obese:** classifies the person's obesity condition based on his BMI as "Yes" or "No"

First, the variables of interest are selected from the `brfss2013` database and cleaned to remove the cells with "NA":
```{r R3: Selecting variables of interest}
# Selecting variables of interest

df3<-brfss2013[,c("weight2", "height3", "X_ageg5yr", "diabete3")]
df3 <- df3 %>%
filter(!is.na(weight2), !is.na(height3), !is.na(diabete3) , !is.na(X_ageg5yr))

summary (df3)
```

From the summary table, it is evident that:

1. The `weight2` variable is a categorical variable which needs to be converted into a numeric variable. 

2. The `diabete3` variable needs to be reduced from the existing 4-levels to 2-levels. (new variable: `diabetic`)

```{r Converting weight variable to a numeric variable}

# Converting weight variable to a numeric variable

df3<-df3 %>%
filter(str_detect(weight2,"1")|str_detect(weight2,"2")|str_detect(weight2,"3")|str_detect(weight2,"4")|str_detect(weight2,"5")|str_detect(weight2,"6")|str_detect(weight2,"7")|str_detect(weight2,"8")|str_detect(weight2,"9")|str_detect(weight2,"0"))

df3$weight2<-df3$weight2%>%
as.numeric(as.character(df3$weight2))

df3<-df3%>%
mutate(diabetic = ifelse(diabete3 =="Yes","Yes","No"))

str(df3)
```

Next we convert:

1. `weight2`, currently available in pounds or kgs into a new variable, `wt_kgs` which gives the weight in kgs.

2. `height3`, currently available in ft-inches or meters into a new variable, `ht_mtrs` which gives the height in meters.

```{r Converting weights to kgs & heights to meters}

# Converting weights to kgs & heights to meters

df3 <- df3 %>%
mutate(wt_kgs = round((weight2/2.2),1))

df3 <- df3 %>%
mutate(ht_mtrs = ifelse(height3 < 1000,round({(height3%/%100)*0.3048+(height3%%100)*.0254},3),round({(height3%%1000)/100},3)))

```


Using the variables `wt_kgs` & `ht_mtrs`, we calculate the `BMI` for each reading and review the output data.
```{r Calculating BMI}
# Calculating BMI

df3 <- df3 %>%
mutate(BMI = round((wt_kgs/ht_mtrs^2),1))

```

Next we select the valid range of BMI values based on the data provided in [CDC's,Anthropometric reference data for children and adults; United States, 2011-2014](https://stacks.cdc.gov/view/cdc/40572). Based on this report we conclude that the valid range for `BMI` is (19.3, 50) & all values out of this range might be due to an error in data entry.

Further based on the `BMI` values, we label the reading with `BMI` > 30 as `obese` = "Yes" and `BMI` < = 30 as `obese` = "No"

```{r Determining whether an individual is Obese}

# Determining whether an individual is Obese

df3<- df3%>%
filter(BMI>19.3, BMI<50)

df3<- df3%>%
mutate(obese = ifelse(BMI > 30,"Obese = Yes","Obese = No"))

```

**P2: Data Analysis:**

Based on the final subset of data thus obtained, we plot "Stacked bar-plots":

```{r Side-by-side Bar plot, Obesity Vs Diabetic}
# Side-by-side Bar plot, Obesity Vs Diabetic

ggplot(df3, aes(x=obese, fill = diabetic)) + 
geom_bar(position="fill", width = 0.6, color="black", size=0.5, alpha = 0.7) + facet_wrap( ~ X_ageg5yr, ncol=5)+ theme(legend.position = "right", axis.text.x = element_text(angle=90, hjust = 0.8))+ labs(x="Obesity", y="Percentage Diabetic", title="Obesity vs Diabetic")+scale_y_continuous(labels = scales::percent)

```

**Plot 1: Obesity vs Diabetic:** 

**Summary 3.1:** Analyzing the plot we can conclude that the percentage of diabetic people increases if the population is obese, thus suggesting that **obese people are more prone to being diabetic.**

```{r Side-by-side Bar plot, Age Vs Diabetic}
# Side-by-side Bar plot, Age Vs Diabetic

ggplot(df3, aes(x=X_ageg5yr, fill = diabetic)) + geom_bar(position="fill", width = 0.6, color="black", size=0.5, alpha = 0.7) + facet_wrap( ~ obese, ncol=5)+theme_minimal()+ theme(legend.position = "right", axis.text.x = element_text(angle=90, hjust = 0.8))+ labs(x="Age of person", y="Percentage Diabetic", title="Age vs Diabetic")+ scale_y_continuous(labels = scales::percent)
```

**Plot 2: Age vs Diabetic:** 

**Summary 3.2:** It is evident from the plot that irrespective of whether a person is obese or not, the risk of developing diabetes increases with the person's age. Thus suggesting, **one’s age increases the risk of developing diabetes.**